A Case Study in Preserving a\\High Energy Physics Application

### 2014-12-08 paper.tex
add subtitle and remove copyright info.
Modify acknowledgement
Add network_tracking_parrot into paper.tex (section 5.1)

\documentclass{sig-alternate}
\usepackage{url}
\usepackage[flushleft]{threeparttable}
\hyphenation{resour-ces}
\hyphenation{approac-hes}
\hyphenation{har-der}
\hyphenation{spe-cifically}
\begin{document}

\title{A Case Study in Preserving a\\High Energy Physics Application}
\author{
Haiyan Meng, Matthias Wolf, Peter Ivie, Anna Woodard, Michael Hildreth, and Douglas Thain\\
\affaddr{Department of Physics and Department of Computer Science and Engineering}\\
\affaddr{University of Notre Dame}\\
\affaddr{\{hmeng|mwolf3|pivie|awoodard|mhildret|dthain\}@nd.edu}
}
\date{15 January 2014}
\maketitle

@@

@@

This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
OCI-1148330 (SI2) and PHY-1312842.
The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.
\bibliographystyle{abbrv}
\bibliography{cclpapers,this}

>>>>

\documentclass{sig-alternate}
\usepackage{url}
\usepackage[flushleft]{threeparttable}
\hyphenation{resour-ces}
\hyphenation{approac-hes}
\hyphenation{har-der}
\hyphenation{spe-cifically}
\makeatletter
\def\@copyrightspace{\relax}
\makeatother
\begin{document}

\title{A Case Study in Preserving a\\High Energy Physics Application}
\subtitle{DASPOS Technical Report \#2}
\author{
Haiyan Meng, Matthias Wolf, Peter Ivie, Anna Woodard, Michael Hildreth, and Douglas Thain\\
\affaddr{Department of Physics and Department of Computer Science and Engineering}\\
\affaddr{University of Notre Dame}\\
\affaddr{\{hmeng|mwolf3|pivie|awoodard|mhildret|dthain\}@nd.edu}
}
\date{15 January 2014}
\maketitle

@@

\subsection{Tracking of Network Dependencies}

\begin{figure}
\centering
\includegraphics[width=1\columnwidth]{git-syscall.eps}
\caption{Exec Syscalls of a git command}
\label{fig:git-syscall}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\columnwidth]{http_packet.eps}
\caption{HTTP Request and Response}
\label{fig:http_packet}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\columnwidth]{url_redirection.eps}
\caption{An Example of URL Redirection}
\label{fig:url_redirection}
\end{figure}

All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g. http, https and ssh).
Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications. A URL which works normally today may be unavailable permanently. A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters. However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes. Figure~\ref{fig:git-syscall} shows all the processes created by a git command. A process with PID 998 is created to clone a remote git repository into local machine, which totally has 6 child processes. Moreover, a network-relevant executable name collection is necessary to identify network dependencies. The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.

Another solution to track network dependencies is to track the network sockets. The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux. From the process tree shown in the above figure, the process with PID 1000 responds to create a socket, connect to a DNS server, send a DNS request packet to the DNS server and receive a DNS response packet from the DNS server. The information gained from the network socket tracking can be divided into three categories.
\begin{itemize}
\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6). 
\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}. However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data. 
\end{itemize}

The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
\begin{itemize}
\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional. A DNS response packet with the type CNAME has multiple answers. For example, the DNS response packet which tries to resolve {\tt www3.nd.edu} includes two answers. The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address. 
{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url. Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}. Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol. 
\end{itemize}

The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible. All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.

@@

This work was supported in part by National Science Foundation grants PHY-1247316 (DASPOS), 
OCI-1148330 (SI2) and PHY-1312842.
The University of Notre Dame Center for Research Computing scientists and engineers provided critical technical assistance throughout this research effort.

Copyright (C) 2014 The University of Notre Dame

This work is licensed under the Creative Commons Attribution 4.0 License.

\bibliographystyle{abbrv}
\bibliography{cclpapers,this}
